A survey of HTTP caching implementations on the open Semantic Web

### 2015-03-11 sanity/paper1.tex
contributions
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@1060 43ef1190-90fd-4dd7-a769-d0121f02b80e

In spite of this, we have not seen it in widespread use in the
Semantic Web, and therefore we decided to conduct a survey to
investigate the actual compliance to RFC7234 and RFC7232. 
With this paper, we hope to achieve the following:\todo{formulate as contributions}
\begin{enumerate}
\item Understand the actual usage rather than rely on anecdotal
  conceptions.
\item Encourage the implementation of these mechanisms in Semantic Web
  infrastructure.
\item Point out future research directions.
\end{enumerate}

>>>>

In spite of this, we have not seen it in widespread use in the
Semantic Web, and therefore we decided to conduct a survey to
investigate the actual compliance to RFC7234 and RFC7232. 
The objectives of this paper are:
\begin{enumerate}
\item Understand the actual usage rather than rely on anecdotal
  conceptions.
\item Encourage the implementation of these mechanisms in Semantic Web
  infrastructure.
\item Point out future research directions.
\end{enumerate}
The contributions of this paper are to meet these objective by means
of a survey that shows that while the uptake has been moderate,
practical benefits may be realized already. Based on this survey as
well as practical experience, we point out future research directions
as well as some recommendations for deployed implementations.
